The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-09 rockerverse.Rmd
add ó for @daroczig
Update rockerverse.Rmd

  - name: Gergely Daroczi

@@

    affiliation: IIH Nordic A/S, Google Developer Expert for GCP

@@

@@

@@

# some functionalities might be missing. please add them if you find that any are missing!
package_functionalities <- tribble(
  ~package, ~id,
  "harbor", c("execute", "cloud", "images"),
  "stevedore", c("api", "execute", "cloud", "images", "interact"), # build?
  "AzureContainers", c("build", "execute", "cloud"),
  "babelwhale", c("execute", "interact", "othercontainers"),
  "dockyard", c("dockerfile", "build", "execute"), # cloud?
  "dockermachine", c("install", "execute", "cloud", "interact")
)

@@

**\pkg{dockermachine}** ([https://github.com/cboettig/dockermachine](https://github.com/cboettig/dockermachine)) is an R package to provide a convenient interface to [Docker&nbsp;Machine](https://docs.docker.com/machine/overview/) from R.
The CLI tool `docker-machine` allows users to create and manage a virtual host on local computers, local data centers, or at cloud providers.
A local Docker installation can be configured to transparntly forward all commands issued on the local Docker CLI to a selected (remote) virtual host.
Docker&nbsp;Machine was especially crucial for local use in the early days of Docker, when no native support was available for Mac or Windows computers, but it remains relevant for provisioning on remote systems.
The package has not received any updates for two years, but it is functional with a current version of `docker-machine` (`0.16.2`).
It potentially lowers the barriers for R users to run containers on various hosts if they perceive that using the Docker&nbsp;Machine CLI directly as a barrier and it enables scripted workflows with remote processing.

>>>>

  - name: Gergely Daróczi

@@

    # https://github.com/MarkEdmondson1234
    affiliation: IIH Nordic A/S, Google Developer Expert for Google Cloud Platform

@@

      - Artillerivej 86
      - 2300 København S, Denmark
      - \orcid{0000-0002-8434-3881}

@@

      - \orcid{0000-0002-2136-0000}

@@

# some functionalities might be missing. please add them if you find that any are missing!
package_functionalities <- tribble(
  ~package, ~id,
  "harbor", c("execute", "cloud", "images"),
  "stevedore", c("api", "execute", "cloud", "images", "interact"), # build?
  "AzureContainers", c("build", "execute", "cloud"),
  "babelwhale", c("execute", "interact", "othercontainers"),
  "dockyard", c("dockerfile", "build", "execute"), # cloud?
  "dockermachine", c("install", "execute", "cloud", "interact"),
  "googleCloudRunner", c("build", "execute", "cloud")
)

@@

**\pkg{dockermachine}** ([https://github.com/cboettig/dockermachine](https://github.com/cboettig/dockermachine)) is an R package to provide a convenient interface to [Docker&nbsp;Machine](https://docs.docker.com/machine/overview/) from R.
The CLI tool `docker-machine` allows users to create and manage a virtual host on local computers, local data centers, or at cloud providers.
A local Docker installation can be configured to transparently forward all commands issued on the local Docker CLI to a selected (remote) virtual host.
Docker&nbsp;Machine was especially crucial for local use in the early days of Docker, when no native support was available for Mac or Windows computers, but it remains relevant for provisioning on remote systems.
The package has not received any updates for two years, but it is functional with a current version of `docker-machine` (`0.16.2`).
It potentially lowers the barriers for R users to run containers on various hosts if they perceive that using the Docker&nbsp;Machine CLI directly as a barrier and it enables scripted workflows with remote processing.
